Title: A proof-of-concept study

### 2022-01-25 paper.tex
update

\section{Introduction}
Early attempts to model the Fermi bubbles assumed that the jet is vertial to the Galactic plane...

@@

  \begin{figure*}
    \subfigure[Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
               (photons s$^{-1}$ deg$^{-2}$) in the 0.6-1.0 keV range,\
               using a Hammer-Aitoff projection. Throughout this paper we show sky maps\
               in Galactic coordinates centered on the Galactic center and observed by the poistion of the Sun.\
               The red arrow at the center of the\
               top panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
               to the disk normal in 1.2 Myr.]
     {
      \includegraphics[width=0.8\linewidth]{figures/fig__xraymap.png}
      \label{fig__xray_0.8keV_angle_000}
     }
    \subfigure[Comparison of observed (black; \citealt{Predehl2020}) and simulated (red) one-dimensional\
               count rate profiles in the same energy band as \Cref{fig__xray_0.8keV_angle_000},\
               cut at various galactic latitudes (as labelled).]
     {
      \includegraphics[width=\linewidth]{figures/fig__xray-profile-0.8keV-000.png}
      \label{fig__x-ray-profile-0.8keV-000}
     }
    \caption{}
    \label{fig_xray}
  \end{figure*}

@@

\subsubsection{Leptonic process}
In the leptonic scenario, the gamma-rays originate from IC scattering of the ISRF by CRe.\
The CRe spectrum follows a power law distribution\
with a spectral index $p=2.4$ \citep{Selig2015} and ranges from\
$m_{\text{e}}c^2$ ($0.5$ MeV) to $10^{6}m_{\text{e}}c^2$ ($0.5$ TeV).\

@@

\begin{figure*}
  \includegraphics[width=\linewidth]{figures/fig__GammaRay_100e9_1e6_angle_000.png}
  \caption{The observed (left) and simulated (right) photon flux at 108.6 GeV.\
           Note that the panel on left side is diffuse (i.e. no point-like component)\
           photon flux reconstructed by the D$^3$PO algorithm \citep{Selig2015} that analyze\
           the photon data from the \textit{Fermi} Large Area Telescope \citep{Atwood2009}.
  }
  \label{fig__gammaRay}
\end{figure*}

@@

\appendix

>>>>

\section{Introduction}
The \textit{Fermi} bubbles, two giant bubbles extending about 50 degrees above and below the Galactic center (GC),\
are among the most important findings of the Fermi Gamma-ray Space Telescope\

Early attempts to model the Fermi bubbles assumed that the jet is vertial to the Galactic plane...

@@

  \begin{figure*}
    \subfigure[Simulated (top) and observed (bottom; \citealt{Predehl2020}) count rate\
               (photons s$^{-1}$ deg$^{-2}$) in the 0.6-1.0 keV range,\
               using a Hammer-Aitoff projection. Throughout this paper we show sky maps\
               in Galactic coordinates centered on the Galactic center and observed by the solar position.\
               The red arrow at the center of the\
               top panel depicts the direction of the bipolar jet, constantly ejecting at an angle of $45^{\circ}$\
               to the disk normal in 1.2 Myr.]
     {
      \includegraphics[width=0.8\linewidth]{figures/fig__xraymap.png}
      \label{fig__xray_0.8keV_angle_000}
     }
    \subfigure[Comparison of observed (black; \citealt{Predehl2020}) and simulated (red) one-dimensional\
               count rate profiles in the same energy band as \Cref{fig__xray_0.8keV_angle_000},\
               cut at various galactic latitudes (as labelled).]
     {
      \includegraphics[width=\linewidth]{figures/fig__xray-profile-0.8keV-000.png}
      \label{fig__x-ray-profile-0.8keV-000}
     }
    \caption{}
    \label{fig_xray}
  \end{figure*}

@@

\subsubsection{Leptonic process}
In the leptonic scenario, the gamma-rays originate from IC scattering of the ISRF by CRe.\
The CRe spectrum follows a power law distribution\
with a spectral index $p=2.4$ and ranges from\
$m_{\text{e}}c^2$ ($0.5$ MeV) to $1.1\times10^{6}m_{\text{e}}c^2$ ($0.55$ TeV).\

@@

\begin{figure*}
  \includegraphics[width=\linewidth]{figures/fig__GammaRay_100e9_1e6_angle_000.png}
  \caption{The observed (left) and simulated (right) photon flux at 108.6 GeV.\
           Note that the left panel is the\
           photon flux of the diffuse component reconstructed by the D$^3$PO algorithm \citep{Selig2015} that analyzes\
           the photon data from the \textit{Fermi} Large Area Telescope \citep{Atwood2009}\
           and removes the contribution from point-like component.
  }
  \label{fig__gammaRay}
\end{figure*}

@@

%\appendix
